### 2017-01-24 main.tex
Some changes for editorial comment #2 (compensate for their citation style's failings).

This consistency allows a variety of experiments if precise moments in
song can reliably be detected quickly enough to trigger other
apparatus during singing.  A common area of study with this
song-triggering technique is the anterior forebrain pathway (AFP), a
homologue of mammalian basal ganglia consisting of a few distinct
brain areas concerned with the learning and production of song.  For
example, \cite{Kao2005} stimulated the lateral magnocellular nucleus
of the anterior nidopallium (LMAN)---the output nucleus of the
AFP---at precisely timed moments during song and showed that this area
repeatably controls specific variables in song output.
\cite{Wang2008interhemispheric} stimulated LMAN and the high vocal
centre (HVC) in one hemisphere or the other, and found that control of
song rapidly switches between hemispheres.  \cite{Keller2009}
investigated the response of cells in field L and the caudolateral
mesopallium during song with and without feedback perturbations as
well as external sounds, and concluded that these regions may hold a
representation of song against which auditory signals are compared.
\cite{Tumer2007pitchshift} played a disruptive sound during renditions
of a syllable that were slightly above (or below) its average pitch,
and showed that the presence of this apparently random natural
variability in songbird motor output is used to drive change in the
song.  \cite{Andalman2009} extended this experiment and showed that
AFP produces a corrective signal to bias song away from those
disruptions.  \cite{Charlesworth2011learning} showed that the song
change was isolated to within roughly 10 milliseconds (ms) of the
stimulus, and further proposed an elegant model that predicts the
shape of the learned response and suggests a simple mechanism.
\cite{Warren2011} showed that that AFP transfers the error signal to
the robust nucleus of the arcopallium (RA) using
NMDA-receptor--mediated glutamatergic transmission. By looking at song
recovery after applying the same pitch-shift paradigm,
\cite{Canopoli2014} showed that the caudal medial nidopallium is
implicated in memorising or recalling a recent song target, but for
neither auditory processing nor directed motor learning.

@@

Despite the power and versatility of vocal feedback experiments, there
is no standard syllable detector.  Desiderata include:
\begin{description}
\item[Accuracy:] How often does the system produce false positives or false negatives?
\item[Latency:] The average delay between the target syllable being sung and the detection.
\item[Jitter:] The amount that latency changes from instance to instance of song.  Our measure of jitter is the standard deviation $\sigma$ of latency.
\item[Versatility:] Is detection possible at ``difficult'' syllables?
\item[Ease of use:] How automated is the process of programming a detector?
\item[Cost:] What are the hardware and software requirements?
\end{description}

@@

\begin{enumerate}
\item Record and align a corpus of training songs.  The technique has been published in \cite{Poole2012}.
\item Choose one or more instants in the song that should create a trigger event, and train a
  neural network to recognise them. This step is carried out offline.  While any neural network software would produce equivalent results, we used MATLAB 2015b's neural network toolbox.
\item Once trained and saved, the neural network is used by a realtime
  detection program that listens to an audio signal and indicates detection of the target
  syllables via a TTL pulse.  We present three implementations, in MATLAB, LabVIEW, and Swift, that trade off hardware requirements, ease of maintenance, and performance.
\end{enumerate}
This method makes the following contributions:
\begin{itemize}
\item Fast: sub-millisecond latencies, with jitter around 2 ms.
\item Accurate: false negative rates under 1\% and false positive rates under 0.001\% for a variety of syllables.  Balancing these rates depends on a single relative-cost parameter.
\item State-of-the-art performance with default parameters.
\item Runs on inexpensive hardware.
\item Described in detail here, with reference implementations provided and benchmarked.
\end{itemize}

@@

This implementation requires special software and hardware: LabVIEW
from National Instruments---we used 2014 service pack 1---and a data acquisition card---we use the
National Instruments PCI-6251 card on a PC with an Intel Core i5-4590
processor at 3.7GHz (a relatively low-end machine) with 32 gigabytes
of RAM, running Microsoft Windows 8.1 Pro.

This implementation has several drawbacks: it requires Windows and
expensive hardware and software and due to the programming language it
is difficult to modify and debug---indeed, a persistent bug in our
implementation currently renders it substantially less accurate than
the other detector implementations on some syllables. However, our
test configuration usually achieved excellent performance, and further
gains should be possible if the implementation were retargeted onto
field-programmable gate array (FPGA) hardware---which would have the additional benefit of providing
deterministic ``hard realtime'' guarantees---or just run on a faster
desktop system.

@@

% A:
% B: LNY46 0.28s
% C: LNY42 0.38s
% D: LNY4RB 0.25s

@@

\begin{table}
  \begin{tabular}{c|cccc}
    Bird & Training songs & Test songs & Training non-song & Test non-song \\ \hline
    A & 1000 & 1818 & 1000 & 3636 \\
    B & 1000 & 1533 & 158 & 242 \\
    C & 1000 & 1245 & 178 & 222 \\
    D & 1000 & 1614 & 153 & 247
  \end{tabular}
  \caption{Sizes of our training and test sets.}
  \label{table:datasizes}
\end{table}

>>>>

If precise moments in song can reliably be detected quickly enough to
trigger other apparatus during singing, then this consistency of
behaviour allows a variety of experiments.  A common area of study
with this song-triggering technique is the anterior forebrain pathway
(AFP), a homologue of mammalian basal ganglia consisting of a few
distinct brain areas concerned with the learning and production of
song.  For example, stimulation of the lateral magnocellular nucleus
of the anterior nidopallium (LMAN)---the output nucleus of the
AFP---at precisely timed moments during song shows that this area
controls specific variables in song output \cite{Kao2005}.
Song-synchronised stimulation of LMAN and the high vocal centre (HVC)
in one hemisphere or the other showed that control of song rapidly
switches between hemispheres \cite{Wang2008interhemispheric}.
Feedback experiments have shown that Field L and the caudolateral
mesopallium may hold a representation of song against which auditory
signals are compared \cite{Keller2009}.  Renditions of a syllable that
were disrupted by white noise when they were slightly above (or below)
its average pitch showed that the apparently random natural
variability in songbird motor output is used to drive change in the
song \cite{Tumer2007pitchshift}. Furthermore, AFP produces a
corrective signal to bias song away from those disruptions
\cite{Andalman2009}. The
song change is isolated to within roughly 10 milliseconds (ms) of the
stimulus , and further proposed an elegant model that predicts the
shape of the learned response and suggests a simple mechanism \cite{Charlesworth2011learning}.

\cite{Warren2011} showed that that AFP transfers the error signal to
the robust nucleus of the arcopallium (RA) using
NMDA-receptor--mediated glutamatergic transmission. By looking at song
recovery after applying the same pitch-shift paradigm,
\cite{Canopoli2014} showed that the caudal medial nidopallium is
implicated in memorising or recalling a recent song target, but for
neither auditory processing nor directed motor learning.

@@

Despite the power and versatility of vocal feedback experiments, there
is no standard syllable detector.  Desiderata for such a detector include:
\begin{description}
\item[Accuracy:] How often does the system produce false positives or false negatives?
\item[Latency:] The average delay between the target syllable being sung and the detection.
\item[Jitter:] The amount that latency changes from instance to instance of song.  Our measure of jitter is the standard deviation $\sigma$ of latency.
\item[Versatility:] Is detection possible at ``difficult'' syllables?
\item[Ease of use:] How automated is the process of programming a detector?
\item[Cost:] What are the hardware and software requirements?
\end{description}

@@

\begin{enumerate}
\item Record and align a corpus of training songs.  The technique has been published in \cite{Poole2012}. 200 songs generally yield acceptable results, but here we standardise on 1000-song training sets.
\item Choose one or more instants in the song that should create a trigger event, and train a
  neural network to recognise them. This step is carried out offline.  While any neural network software would produce similar results, we used MATLAB 2015b's neural network toolbox.
\item Once trained and saved, the neural network is used by a realtime
  detection programme that listens to an audio signal and indicates detection of the target
  syllables via a TTL pulse.  We present three implementations, in MATLAB, LabVIEW, and Swift, that trade off hardware requirements, ease of maintenance, and performance.
\end{enumerate}
This method makes the following contributions:
\begin{itemize}
\item Fast: sub-millisecond latencies, with jitter around 2 ms.
\item Accurate: false negative rates under 1\% and false positive rates under 0.001\% for a variety of syllables.
\item State-of-the-art performance with default parameters.
\item Requires almost no programming experience.
\item Runs on inexpensive hardware.
\item Described in detail here, with reference implementations provided and benchmarked.
\end{itemize}

@@

This implementation requires special software and hardware: LabVIEW
from National Instruments---we used 2014 service pack 1---and a data acquisition card---we use the
National Instruments PCI-6251 card on a PC with an Intel Core i5-4590
processor at 3.7GHz (a relatively low-end machine) with 32 gigabytes
of RAM, running Microsoft Windows 8.1 Pro and Windows 10.

This implementation has several drawbacks: it requires expensive hardware and software from National Instruments (a data acquisition card and LabVIEW), Windows (we use hardware features of LabVIEW that are unavailable on MacOS or Linux), and due to the programming language it
is difficult to modify and debug---indeed, a persistent bug in our
implementation currently renders it substantially less accurate than
the other detector implementations on some syllables. However, our
test configuration proved itself capable of excellent performance, and further
gains should be possible if the implementation were retargeted onto
field-programmable gate array (FPGA) hardware---which would have the additional benefit of providing
deterministic ``hard realtime'' guarantees---or just run on a faster
desktop system.

@@

% A:
% B: LNY46 0.28s @ 140ms
% C: LNY42 0.38s
% D: LNY4RB 0.25s

@@

\begin{table}
  \begin{tabular}{c|cccc}
    Bird & Training songs & Test songs & Training non-song & Test non-song \\ \hline
    A & 1000 & 1818 & 1000 & 3636 \\
    B & 1000 & 1530 & 1428 & 2185 \\
    C & 1000 & 1245 & 990 & 1233 \\
    D & 1000 & 1614 &  & 247
  \end{tabular}
  \caption{Sizes of our training and test sets.}
  \label{table:datasizes}
\end{table}
